---
title: "Statistician case study"
author: "Solomon Nganga"
date: "`r Sys.time()`"
output:
  word_document: default
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
library(broom)
library(janitor)
library(patchwork)
library(tidyverse)
library(scales)

data <- read_csv("Statistician_Case_Study_Data.csv")
```

```{r pre-processing, include=FALSE}
dt <- data %>% 
  clean_names() %>% 
  pivot_longer(
    cols = starts_with("is_disabled_w"),
   names_to = "disable_track_wk",
   names_prefix = "is_disabled_w",
   values_to = "disabled_status",
   values_drop_na = TRUE
 ) %>% 
  pivot_longer(
    cols = starts_with("frr_w"),
   names_to = "frr_track_wk",
   names_prefix = "frr_w",
   values_to = "frr_value",
   values_drop_na = TRUE
 )

```


## Greenlight Planet Pilot Presentation.

Greenlight Planet sells lamps and TVs that are repaid over time by its customers.

## Background

### Trends in the disabled rates

We are going to do some exploration of the pilot study and have a look at the the evolution over time of the disabled rates for Country 1 with/without treatment and Country 2 
 
```{r echo=FALSE}
# Another Idea
dt1 <- dt %>% 
  filter(disabled_status == "Yes") %>% 
  mutate(disabled_status_per_country = case_when(country == "Country 1" &
                                        is_treatment == "Yes" ~ "Country1_with_Treatment", 
                                        country == "Country 1" &
                                        is_treatment == "No" ~ "Country1_without_Treatment",
                                        country == "Country 2" ~ "Country2"))

#the plot
dt1 %>% 
  count(disabled_status_per_country, disable_track_wk,name = "frequency") %>%  
  mutate(percentage = round(frequency/sum(frequency),4)*100) %>% 
  arrange(desc(percentage)) %>% 
  mutate(disable_track_wk =fct_reorder(disable_track_wk,frequency)) %>%
  ggplot(aes(x = disable_track_wk ,y = percentage, fill = disabled_status_per_country))+ geom_col(position = "dodge")+
  labs(x = "weeks of follow up", y = "percentage frequency", title = "How does treatment affect disabling rates?", subtitle = "Country 2 showed the highest disable rate of 18.2%\n the treament might have led to a very low disabling rate for country 1\n i.e, 0.22% as compared to without treatment that had,\n 1.54% overall disabling rate.") +
  theme_bw() +
  scale_y_continuous(
  breaks = c(0, 5,10,15, 20),
  label = c("0%", "5 %", "10 %","15 %", "20 %")
) +
  scale_x_discrete(
    label = c("week2", "week4","week6", "week8", "week10")
  )

#the table explaining the plot
dt1 %>%
  count(disabled_status_per_country, disable_track_wk,name = "frequency") %>%
  mutate(percentage = round(frequency/sum(frequency),4)*100) %>%
  group_by(disabled_status_per_country) %>%
  summarise(avr_perc = mean(percentage)) %>%
  arrange(desc(avr_perc)) %>% 
  mutate(avr_perc = avr_perc/100,
         avr_perc = percent(avr_perc)) %>% 
  knitr::kable(caption = "Table showing overall percentage of disable rates per country", col.names = c("Disabled Status of country","perc disable rate"), 
               align = "lr")

```



### Trend in the disabled FRR

The evolution over time of the FRR for Country 1 with/without treatment 

```{r preprocessing frr, echo=FALSE}
#creating a new variable for treatment.
dt2 <- dt %>% 
  mutate(frr_status_country = case_when(country == "Country 1" &
                                        is_treatment == "Yes" ~ "Country1_with_Treatment", 
                                        country == "Country 1" &
                                        is_treatment == "No" ~ "Country1_without_Treatment",
                                        country == "Country 2" ~ "Country2"))

```


```{r echo=FALSE}
#plotting the graph for Frr
dt2 %>%
    group_by(frr_status_country, frr_track_wk) %>% 
  summarize(average = mean(frr_value)) %>% 
  mutate(frr_track_wk = fct_reorder(frr_track_wk, average)) %>% 
  ggplot(aes(frr_track_wk, average , fill = frr_status_country)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = dollar_format()) +
  labs(x = "weeks of follow up", y = "average frr in millions", title = "What is the trend of average frr per week per country?", subtitle = "Country 1 with treatment showed a 15.7% increase in total frr\n, followed by a 12% increase in without treatment\n and finally Country 2 had a 10.9% increase in total frr. ") +
  theme_bw() +
  scale_x_discrete(
    label = c("week2", "week4","week6", "week8", "week10")
  ) 
  
#the stats for frr by country
dt2 %>%
group_by(frr_status_country) %>%
summarize(overall_average = mean(frr_value) * 1000000) %>% 
  mutate(overall_average = dollar(overall_average)) %>% 
  knitr::kable(caption = "table showing the overall average in frr i millions across each country in the pilot survey",
               col.names = c("names","Average frr value"), 
               align = "lr")
```

### Comparison test

We going to run analysis of variance test on the means of the metrics. We initially assume that the metrics per country are the same, but we are going to try to prove this!!!

We are going to do this using individual t_test within groups. This is very important because we need to see which

```{r echo=FALSE}
#for Disable rate
# dt1 %>% 
#   count(disabled_status_per_country, disable_track_wk,name = "frequency") %>%  
#   mutate(percentage = round(frequency/sum(frequency),4)*100) %>% 
#   arrange(desc(percentage)) %>% 
#   group_by(disabled_status_per_country) %>% 
#   summarize(t_test = list(t.test()))


  
#for frr by week
dt2 %>% 
  group_by(frr_status_country, frr_track_wk) %>% 
  summarize(t_test = list(t.test(frr_value))) %>% 
  mutate(tidied = map(t_test,mu = 0.57, tidy)) %>% 
  unnest(tidied) %>% 
  mutate(frr_track_wk = fct_reorder(frr_track_wk, estimate)) %>% 
  ggplot(aes(estimate, frr_track_wk)) +
  geom_point()+
  geom_errorbarh(aes(xmin = conf.low,
                     xmax = conf.high)) +
  labs(y = " ") +
  facet_wrap(
    ~frr_status_country)
dt2 %>% 
  group_by(frr_status_country, frr_track_wk) %>% 
  summarize(t_test = list(t.test(frr_value))) %>% 
  mutate(tidied = map(t_test,mu = 0.57, tidy)) %>% 
  unnest(tidied) %>% 
  select(1:2,4,conf.low,conf.high, method)

```

